Notes on scheduling the SAA2019 meeting

### 2018-01-10 analysis/paper/saa2018_nonposter_sessions_while_loop.Rmd
move to SAA folder

# prepare some variables... get all the sessions, 
# but we're going to modify this, so make a copy
org_and_gen_session_durations$session_time_allowed <- 
  as.numeric(org_and_gen_session_durations$TIME)
all_nonposter_sessions_with_session_durations$session_time_allowed <- 
  all_nonposter_sessions_with_session_durations$TIME
z7 <- all_nonposter_sessions_with_session_durations
all_of_the_day_parts <- NULL
total_cap$hours_of_sessions <- 0
total_cap$n_sessions <- 0
total_cap$c_sessions <- 0
container_for_this_day_part_with_day_from_while <- 0
i <- 1

@@

       # print(progress_check)

@@

 # # progress check
 print(glue('i = {i}'))
 # 
 # print(
 # all_of_the_day_parts %>% 
 #   group_by(day_part_from_while) %>% 
 #   summarise(papers = n(),
 #             sessions = length(unique(`Session Id`))))

>>>>

# prepare some variables... get all the sessions, 
# but we're going to modify this, so make a copy
org_and_gen_session_durations$session_time_allowed <- 
  as.numeric(org_and_gen_session_durations$TIME)
all_nonposter_sessions_with_session_durations$session_time_allowed <- 
  all_nonposter_sessions_with_session_durations$TIME
z7 <- # just the sessions IDs
  all_nonposter_sessions_with_session_durations %>% 
  group_by(`Session Id`) %>% 
  distinct(`Session Id`)

all_of_the_day_parts <- NULL
total_cap$hours_of_sessions <- 0
total_cap$n_sessions <- 0
total_cap$c_sessions <- 0
container_for_this_day_part_with_day_from_while <- 0
i <- 1

@@

       print(progress_check)

@@

 # # progress check
 print(glue('i = {i}'))
 # 
 print(
 all_of_the_day_parts %>%
   group_by(day_part_from_while) %>%
   summarise(papers = n(),
             sessions = length(unique(`Session Id`))))
